---
title: "Model Outputs"
output: html_notebook
---
# Load Packages
```{r}
library(tidyverse)
library(sf)
library(sjPlot)
library(sjmisc)
library(stargazer)
library(lme4)
library(lmerTest)
library(sjPlot)
library(sjmisc)
library(ggplot2)

library(ggeffects)
library(performance)
library(jtools)
library(R2MLwiN)
library(lmtest)
## Change path to MLwiN executable as appropriate:
options(MLwiN_path="/Users/shivyucel/Documents/projects/DPhil/Code_Data/mlwin/mlnscript")
```

# Notes
* Parks has the lowest number of observations, removing it leads to model convergence with 5/6 response variables
* Including HDI leads to no convergence, likely due to concentration of data in few adm1s
* Most viable option is including all responses without parks, and all independent variables except HDI


```{r}
# v12 is full model variables
#v17 is new demographic + popdens
mob_vars <- st_read("/Users/shivyucel/Documents/projects/DPhil/Code_Data/data/paper2/india/THI_mobility_heat_w_vars_90_4SD_precip.csv")

#set up dependent variables
mob_vars$residential_difference <- as.numeric(mob_vars$residential_difference)
mob_vars$workplaces_difference <- as.numeric(mob_vars$workplaces_difference)
mob_vars$grocery_pharmacy_difference <- as.numeric(mob_vars$grocery_pharm_difference)
mob_vars$parks_difference <- as.numeric(mob_vars$parks_difference)
mob_vars$retail_difference <- as.numeric(mob_vars$retail_rec_difference)
mob_vars$transit_difference <- as.numeric(mob_vars$transit_difference)
mob_vars$adm1 <- as.factor(mob_vars$adm1)
mob_vars$adm2 <- as.factor(mob_vars$adm2)

mob_vars$month <- as.factor(mob_vars$month)

mob_vars$rain_standard_heat <- as.numeric(mob_vars$rain_standard_heat)
mob_vars$rain_standard_control <- as.numeric(mob_vars$rain_standard_control)

#set up independent variables

#level 1 variables
mob_vars$stage_frac <- as.numeric(mob_vars$stage_frac)

mob_vars$thi_heat <- as.numeric(mob_vars$thi_heat)
mob_vars$thi_centered <- mob_vars$thi_heat - mean(mob_vars$thi_heat)

mob_vars$early_hw <- as.factor(mob_vars$early_hw)

mob_vars$thi_diff <- as.numeric(mob_vars$thi_diff)

mob_vars$HDI <- as.numeric(mob_vars$HDI)
mob_vars$popden_dec <- as.numeric(mob_vars$popdens_de)
mob_vars$HDI_dec <- as.numeric(mob_vars$HDI_dec)
mob_vars$over60_dec <- as.numeric(mob_vars$over60_dec)


mob_vars$weekend <- as.factor(mob_vars$weekend)

mob_vars$coast <- as.factor(mob_vars$coast)

mob_vars$elev_1500m <- as.factor(mob_vars$elev_1500m)


mob_vars$thi_diff_centered <- as.numeric(mob_vars$thi_diff) - mean(mob_vars$thi_heat)

mob_vars$heatwave_dur <- as.factor(mob_vars$heatwave_dur)


```

# Check convergence only with basic explanatory variables
* Converges

```{r}
# Model 1: Try all 6 responses with basic variables
#Converges
model_1 <- runMLwiN(c(residential_difference, workplaces_difference, transit_difference, grocery_pharmacy_difference, retail_difference, parks_difference) ~  
                       1 +
                       heat_temp_centered + temp_diff + 
                       early_hw + heatwave_dur + stage_frac + weekend +
                       
                       (1|location) + (1|heat_ID) + (1|index) ,
                    data = mob_vars, D = "Multivariate Normal",estoptions = list(sort.ignore=TRUE, resi.store=TRUE, maxiter = 30)  )

```
```{r}
model_1
```


```{r}
# Model 2: Add popdens 

model_2 <- runMLwiN(c(residential_difference, workplaces_difference, transit_difference, grocery_pharmacy_difference, retail_difference, parks_difference) ~  
                       1 +
                       heat_temp_centered + temp_diff + 
                       early_hw + heatwave_dur + stage_frac + weekend +
                       popden_dec +
                       
                       (1|location) + (1|heat_ID) + (1|index) ,
                    data = mob_vars, D = "Multivariate Normal",estoptions = list(sort.ignore=TRUE, resi.store=TRUE, maxiter = 30)  )

```
```{r}
model_2
```

```{r}
# Model 3: Add popdens + HDI + age

model_3 <- runMLwiN(c(residential_difference, workplaces_difference, transit_difference, grocery_pharmacy_difference, retail_difference, parks_difference) ~  
                       1 +
                       heat_temp_centered + temp_diff + 
                       early_hw + heatwave_dur + stage_frac + weekend +
                       popden_dec + HDI_dec + over60_dec +
                       
                       (1|location) + (1|heat_ID) + (1|index) ,
                    data = mob_vars, D = "Multivariate Normal",estoptions = list(sort.ignore=TRUE, resi.store=TRUE, maxiter = 30)  )

```

```{r}
# Model 4: Add coast and elevation

low_elev_india_model <- runMLwiN(c(residential_difference, workplaces_difference, transit_difference, grocery_pharmacy_difference, retail_difference, parks_difference) ~  
                       1 +
                       thi_centered + thi_diff + 
                       heatwave_dur + stage_frac + weekend +
                       popden_dec + HDI_dec + over60_dec +
                       coast +  
                       
                       (1|location) + (1|heat_ID) + (1|index) ,
                    data = mob_vars, D = "Multivariate Normal",estoptions = list(sort.ignore=TRUE, resi.store=TRUE, maxiter = 30)  )

```

```{r}
# Model 4: Add coast and elevation

india_model <- runMLwiN(c(residential_difference, workplaces_difference, transit_difference, grocery_pharmacy_difference, retail_difference, parks_difference) ~  
                       1 +
                       thi_centered + thi_diff + rain_standard_heat + rain_standard_control +
                       heatwave_dur + stage_frac + weekend +
                       popden_dec + HDI_dec + over60_dec +
                       coast + elev_1500m + 
                       
                       (1|location) + (1|heat_ID) + (1|index) ,
                    data = mob_vars, D = "Multivariate Normal",estoptions = list(sort.ignore=TRUE, resi.store=TRUE, maxiter = 30)  )

```

```{r}
india_model
```







```{r}
x <- data.frame(india_model@FP)

write.csv(x, file='/Users/shivyucel/Documents/projects/DPhil/Code_Data/data/regression/thi_india_params_4SD_precip.csv')
```



